Brief Announcement: Tight Bounds for Online Balanced Re-Partitioning

### 2020-02-17 paper/podc20ba.tex
ACM comments, done
Fixing acm-format-ref block
\O not displayed apparently

\keywords{online algorithms, competitive analysis, graph partitioning, clustering}

@@

\noindent \textbf{Contributions.}
Our main technical contribution 
is an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the restricted model.
For the online model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $\O(\ell^2)$~\cite{repartition-disc}.
%
Our algorithms can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.

@@

\todo{Author anonymous conference!}

\todo{ACM format for review? Is there any specific format like this? With line numbers etc.}

@@

\todo{ACM Reference format starts with a "." Possibly we did not provide all info}

>>>>

\keywords{online algorithms, competitive analysis, graph partitioning, clustering}
\acmISBN{}\acmPrice{}
\acmDOI{}

@@

\noindent \textbf{Contributions.}
Our main technical contribution 
is an improved lower bound 
of $\Omega(k\cdot\ell)$ on the competitive ratio of any online deterministic online algorithm 
even in the learning model;
the best known lower bound so far was $\Omega(k)$,
even for a more general model~\cite{repartition-disc}.
We also present an asymptotically optimal, 
$O(k\cdot \ell)$-competitive algorithm
for the restricted model.
For the online model, we present  
an asymptotically optimal,
$\Theta(\ell)$ algorithm for $k=3$;
the best known upper bound 
so far was $O(\ell^2)$~\cite{repartition-disc}.
%
Our algorithms can be distributed
similarly to the approach in~\cite{sigmetrics19_partitioning}.

@@

\todo{Author anonymous conference! Done}

\todo{ACM format for review? Is there any specific format like this? With line numbers etc. Done}

@@

\todo{ACM Reference format starts with a "." Possibly we did not provide all info. Done}
